### 2019-09-13 Manuscript/Supplementary_Information/Supplementary_Information.tex
Updates from Overleaf

\begin{SCfigure}[0.6][h!]
\begin{center}
	\includegraphics[width=0.6\textwidth]{../Figures/regolith_schematic.pdf}
	\caption{A schematic representation of the silicate weathering component of GEOCLIM in a single profile at steady-state. A rock particle leaves the unweathered bedrock with production rate $P$, and transits vertically through a regolith of height $h$. Regolith production and physical erosion ($E$) are equal at steady-state. As the particle transits upwards, some fraction of the primary phases ($x$) are chemically weathered ($W$) with the flux of Ca and Mg corresponding to that weathering rate multiplied by the concentration of Ca+Mg in unweathered bedrock ($\chi_{CaMg}$).}
	\label{fig:regolith_schematic}
\end{center}
\end{SCfigure}

@@

\begin{equation}
    \frac{dh}{dt} = P - E
    \label{eq:1}
\end{equation}

\begin{equation}
    \frac{\partial x}{\partial t} = -P \frac{\partial x}{\partial z} - K \tau^{\sigma}x
    \label{eq:2}
\end{equation}

\begin{equation}
    \frac{\partial \tau}{\partial t} = -P \frac{\partial \tau}{\partial z} + 1
    \label{eq:3}
\end{equation}

\noindent
Equation \ref{eq:1} is a statement of material conservation, where $h$ is the total height of the regolith (m), $t$ is the time in the model (yr), $P$ is the regolith production rate (m/yr), and $E$ is the physical erosion rate (m/yr). Equation \ref{eq:2} describes how the residual fraction of weatherable phases ($x$, unitless) changes as a function of time ($t$, yr) and depth (where $z$ is the height above the base of the regolith; m). $K \tau^{\sigma}$ is the dissolution rate constant, which depends on the local climate (captured by $K$, yr$^{-1-\sigma}$) and the time that a given rock particle has spent in the regolith ($\tau$, yr) to some power $\sigma$ (unitless) which implements a time-dependence. Equation \ref{eq:3} describes how the time that a given rock particle has spent in the regolith changes as time in the model progresses.

@@

\begin{equation}
    P = P_{0}\;f(h)
    \label{eq:5}
\end{equation}

@@

\begin{equation}
    E = k_{e}\;q^{m}\;s^{n}
    \label{eq:8}
\end{equation}

@@

\begin{equation}\label{eq:dynsoil_ss}
\left\{\ 
\begin{aligned}
& h   \ =\    \max\left(  \;  0  \;,\;  d_o \log\left(\frac{P_o}{E}\right)  \right)                                                 \\
& x(z)      \ =\   \exp\left(   - \frac{K}{\sigma+1}  \left(\frac{z}{E}\right)^{\sigma+1}   \right)   \\
& W        \ =\   (1-x(h)) \, E  \ =\   (1-x_s) \, E                                                                         \\
\end{aligned}
\right.
\end{equation}

@@

However, as discussed in the main text, $k_{d}$ (Equation \ref{eq:9}), $k_{w}$ (Equation \ref{eq:9}), $\sigma$ (Equation \ref{eq:4}), and $k_{rp}$ (Equation \ref{eq:8}) are poorly constrained. Furthermore, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. We therefore allow these parameters to vary within reasonable bounds during the calibration stage of GEOCLIM (Table \ref{tab:parameter_combinations}).

@@

Finally, although the silicate weathering component of GEOCLIM now implements lithology-dependent Ca+Mg concentration, our implementation does not include lithology-dependent kinetics of mineral dissolution. Relative to felsic lithologies, mafic lithologies contain minerals with faster dissolution kinetics (e.g. olivine and plagioclase; see SI), and thus incorporating lithology-dependent kinetics of mineral dissolution into our simulations would likely increase the sensitivity of steady-state \pCOtwo to increases in subaerially-exposed land area and tectonic topography of I\&NG.

>>>>

\begin{SCfigure}[0.6][h!]
\begin{center}
	\includegraphics[width=0.6\textwidth]{../Figures/regolith_schematic.pdf}
	\caption{A schematic representation of the silicate weathering component of GEOCLIM in a single profile at steady-state. A rock particle leaves the unweathered bedrock with production rate $P_{r}$, and transits vertically through a regolith of height $h$. Regolith production and physical erosion ($E_{p}$) are equal at steady-state. As the particle transits upwards, some fraction of the primary phases ($x$) are chemically weathered ($W$) with the flux of Ca and Mg corresponding to that weathering rate multiplied by the concentration of Ca+Mg in unweathered bedrock ($\chi_{CaMg}$).}
	\label{fig:regolith_schematic}
\end{center}
\end{SCfigure}

@@

\begin{equation}
    \frac{dh}{dt} = P_{r} - E_{p}
    \label{eq:1}
\end{equation}

\begin{equation}
    \frac{\partial x}{\partial t} = -P_{r} \frac{\partial x}{\partial z} - K \tau^{\sigma}x
    \label{eq:2}
\end{equation}

\begin{equation}
    \frac{\partial \tau}{\partial t} = -P_{r} \frac{\partial \tau}{\partial z} + 1
    \label{eq:3}
\end{equation}

\noindent
Equation \ref{eq:1} is a statement of material conservation, where $h$ is the total height of the regolith (m), $t$ is the time in the model (yr), $P_{r}$ is the regolith production rate (m/yr), and $E_{p}$ is the physical erosion rate (m/yr). Equation \ref{eq:2} describes how the residual fraction of weatherable phases ($x$, unitless) changes as a function of time ($t$, yr) and depth (where $z$ is the height above the base of the regolith; m). $K \tau^{\sigma}$ is the dissolution rate constant, which depends on the local climate (captured by $K$, yr$^{-1-\sigma}$) and the time that a given rock particle has spent in the regolith ($\tau$, yr) to some power $\sigma$ (unitless) which implements a time-dependence. Equation \ref{eq:3} describes how the time that a given rock particle has spent in the regolith changes as time in the model progresses.

@@

\begin{equation}
    P_{r} = P_{0}\;f(h)
    \label{eq:5}
\end{equation}

@@

\begin{equation}
    E_{p} = k_{e}\;q^{m}\;s^{n}
    \label{eq:8}
\end{equation}

@@

\begin{equation}\label{eq:dynsoil_ss}
\left\{\ 
\begin{aligned}
& h   \ =\    \max\left(  \;  0  \;,\;  d_{0} \log\left(\frac{P_{0}}{E_{p}}\right)  \right)                                                 \\
& x(z)      \ =\   \exp\left(   - \frac{K}{\sigma+1}  \left(\frac{z}{E_{p}}\right)^{\sigma+1}   \right)   \\
& W        \ =\   (1-x(h)) \, E_{p}  \ =\   (1-x_s) \, E_{p}                                                                         \\
\end{aligned}
\right.
\end{equation}

@@

Of the various parameters used in the equations that govern the silicate weathering component of GEOCLIM (see SI), the values of four parameters within the chemical weathering parameterization of \cite{West2012a} are poorly constrained: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$)

However, the values of four parameters within the chemical weathering parameterization of \cite{West2012a} are poorly constrained: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$; Equation \ref{eq:9}), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$; Equation \ref{eq:9}), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$; Equation \ref{eq:4}), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$; Equation \ref{eq:8}). Furthermore, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. We therefore allow these parameters to vary within reasonable bounds during the calibration stage of GEOCLIM (Table \ref{tab:parameter_combinations}).

@@

Finally, although the silicate weathering component of GEOCLIM now implements lithology-dependent Ca+Mg concentration, our implementation does not include lithology-dependent kinetics of mineral dissolution. Relative to felsic lithologies, mafic lithologies contain minerals with faster dissolution kinetics (e.g. olivine and plagioclase), and thus incorporating lithology-dependent kinetics of mineral dissolution into our simulations would likely increase the sensitivity of steady-state \pCOtwo to increases in subaerially-exposed land area and tectonic topography of I\&NG. We also do not include the effects of reverse weathering \citep{Michalopoulos1995a}, which could modulate the relationship between liberation of Ca and Mg during silicate weathering and long-term \COtwo consumption.
